---
title: "Data Wrangling and Cleaning Practice"
author: "Rachelle"
date: "22 June 2016"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 

# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


```{r}
require(mosaic)
require(dplyr)
require(tidyr)
require(DSR)
data(who)
head(who)
```

```{r}
whoTidy <-
  who %>%
  gather("code","value", 5:60)
whoTidy %>% sample_n(10)
```

```{r}
whoTidy <-
  whoTidy %>%
  separate(code, c("new", "var", "sexage"))
whoTidy %>%
  sample_n(10)
```

```{r}
require(nycflights13)
names(flights)
```

```{r}
names(airports)
```

```{r}
names(airlines)
```

```{r}
names(weather)
names(planes)
```

```{r}
flights %>%
  select(carrier, flight, tailnum, origin, dest)
```

```{r}
airports %>%
  select(faa, name, lat, lon) %>%
  head()
```

```{r}
flights %>%
  inner_join(airports, by = c("dest" = "faa")) %>%
  select(carrier, flight, tailnum, origin, dest, name, lat, lon) %>%
  head()
```

inner_join keeps all the rows from x that have a matching row in y (it's the intersection).
left_join returns all rows from x and appends all columns from x and y.
right_join returns all rows from y and appends all columns from x and y.
full_join gives all the rows and columns from both x and y (it's the union).
anti_join returns all the rows from x where there are not matching values from y.

```{r}
require(lubridate)
rightnow <- now()
day(rightnow)
```

```{r}
yday(rightnow)
```

```{r}
wday(rightnow, label=TRUE)
```

```{r}
wday(rightnow, label=FALSE)
```

```{r}
jan31 <- ymd("2013-01-31")
jan31 + months(0:11)
```

```{r}
floor_date(jan31, "month") + months(0:11) + days(31)
```

```{r}
jan31 %m+% + months(0:11)
```

```{r}
extract_numeric("$1,200.34")
```

```{r}
extract_numeric("-245%")
```

```{r}
install.packages("swirl")
require(swirl)
install_from_swirl(Getting_and_Cleaning_Data)
swirl()
```

